% This is file acknow.tex
\begin{acknowledgment}
\chapter*{Acknowledgments}

Someone once said that editing a multi-author academic treatise is like herding cats. That's probably an understatement; it is at least insulting to cats (who would never lower themselves to being ``herded''). Anyway, I have no idea why anyone would have said that.

In 2004 I asked a number of colleagues who had been instrumental in pulling together the important and extremely useful 1992 University of Arizona Press ``Mars'' book if they knew if anyone was planning to update the part of that tome dealing with the composition, mineralogy, and physical properties of the martian surface, given the major advances in those areas that had occurred in the decade plus since then. No one knew of any such plans, but everyone acknowledged that it would be a challenge, given the continual arrival of new data sets and discoveries and the resulting rapid expansion and evolution of our state of knowledge. Still, perhaps foolishly, I decided that it would be better to at least gather a snapshot of our current view of this topic rather than wait for some ``lull'' in Mars exploration that would allow us all to catch our breath and just spend our time writing papers about what it all means. Indeed, many of us hope that such a lull (like the one from about 1982 through 1997) never happens again (and thus we tacitly accept the challenge of having to write those papers breathlessly\ldots).

In that spirit, my first major acknowledgement is to the more than 100 colleagues who gave me early advice and encouragement or who are the lead authors or co-authors of the chapters in this book. These people are a sample of the community of planetary scientists who are on the ``front lines'' of Mars exploration, having conducted-and in many cases still actively conducting-the investigations, calibrations, experiments, and analyses that are daily modifying our understanding of the Red Planet. Most of these folks (indeed, most scientists nowadays) have frenetic schedules and have to balance huge responsibilities on many levels-mission operations, major laboratories, teaching, management, student mentoring, family\ldots I am indebted to these colleagues for agreeing to take some precious time out of their busy lives to summarize and review recent major results in their areas of specialization. I'm also grateful for their indelible patience in the face of what must often have seemed like incessant nagging from a pesky editor.

Secondly, all of us-editor, authors, readers-are indebted to the dozens of colleagues who provided independent external reviews for all of the chapters of this book. These people also are among the leading experts in Mars studies, and they, too, sacrificed significant time to perform an important community service: making sure that the results and other information in these chapters are accurate (or at least appropriately acknowledged as speculative), complete, and balanced. Specifically, I would like to thank Dave Agresti, Janice Bishop, Bonnie Buratti, David Catling, Ben Clark, Claude d'Uston, Vicky Hamilton, Jim Garvin, Gary Hansen, Lon Hood, Bruce Jakosky, Jeff Johnson, Hugh Kieffer, Melissa Lane, Scott McClennan, Hap McSween, Mike Mischna, Jeff Moersch, Jeff Moore, Dick Morris, Jack Mustard, Horton Newsom, Mike Ramsey, Ken Tanaka, Tim Titus, Alan Treiman, Deanne Rogers, and Ted Roush for each reviewing one or more chapters in this book. Your time and effort have substantially improved this summary and review, and will have hopefully made it a much more useful future resource for students and other researchers new to this field.

Many other people helped to pull this project together, at many stages. I thank Karla Consroe at Cornell University for providing an enormous amount of administrative and editorial assistance. I am also grateful to Bobby Fogel and Marilyn Lindstrom at NASA Headquarters for their initial encouragement of this project, and for helping to secure a small NASA grant (NNX06AH45G) to support some of the administrative costs associated with editing this volume. I also thank Helen Goldrein (Morris), Vince Higgs, and Susan Francis at Cambridge University Press for their constant helpful advice and patience, and for their support for including this book in Cambridge's prestigious Planetary Science series.

Finally, I would like to acknowledge the love and support from my wife Maureen and my children Erin and Dustin. This has been one of my ``Sunday afternoon projects'' for several years now, and it could not have been done without their indulgence and patience with my incessant tippity-tapping at the keyboard during random free moments at home.
\author{Ithaca, NY\hfill Jim Bell\break April, 2007}

\end{acknowledgment}
