
\chapter{Uncivilized United States}

\begin{quotation}
The following article was originally published in the North China Standard of Peking, China, and is furnished to {The New York Times} by the author. 
\end{quotation}

An American,
who was irritated because in an article I wrote lately I had said that the English were the only modern people in the world today who knew how to govern an empire,
said to me,
``what about us Americans?
Although the United States is called a Republic,
yet do we not govern a country as big as the British Empire?''
``Yes,'' I said in reply, ``but there is one great difference between the British people and you Americans.
The British people as a nation is a nation with a civilization,
whereas you Americans, living now in your plaster and concrete sky-scraping tents,
are still a nomad nation without any civilization.''
``oh,'' said the American then to me, angrily and with a sneer,
`` you say that because you have been educated in England and have never been in America!'' 

Indeed. I now remember how a Chinese Minister to America,
the late Chang Yin-huan, who was executed during the Boxer trouble,
once created great astonishment as well as amusement among the Americans in America when he told them that he found everything in America which a man wants except -- religion.
``what，'' said an American newspaper at the time,
``we Americans have no religion -- we, with a church in every street and our missionary societies!
Why, we in America have so much religion that we can afford to export to China and Korea more of that article than any other country!''

Nevertheless, the Chinese Minister, I must say, was quite right in what he said.
Only what he really wanted to say was not that there was no religion,
but that there was no civilization in America.
The real Chinese word for civilization, \emph{li-yo}
(literally ceremony or forms of courtesy and music),
rightly translated by the early Jesuit missionaries as religion,
which the Chinese Minister had in his mind, means both religion and civilization. For, not as in Europe and America today -- where religion is one thing, a something for use only on Sundays, and civilization is quite another thing, a something for use on the other six days of the week -- in China, religion is civilization and civilization is religion; they both mean one and the same thing, namely, form or expression of spiritual life which is for use not only on Sundays, but on every day of a man's life.

But before going further, let me here explain what I mean by a nation with a civilization and a nation without any civilization.
Now we all say that the ancient Greeks and the ancient Romans were great civilized nations.
Why? Because, beside governing and fighting,
besides producing material goods and making money by selling them,
these ancient nations also produced spiritual things such as art and literature and,
what is still more important,
by their art and literature they developed high, perfect types of humanity in their great men
-- all which, now after they have perished and ceased to be nations,
are remembered, admired and prized by men of all after generations.
In short, a civilized nation is a nation which has a spiritual asset or,
as Carlyle calls it. ``realized ideals.'' 

The reason, therefore, why I have said that the British people as a nation is a nation with a civilization is because, besides shopkeeping, winning Waterloo battles and governing an Indian Empire, the British nation, like the ancient Greeks and Romans, has also produced one very great spiritual thing
-- with perhaps one exception, the greatest thing, in my opinion,
which modern Europe has yet produced
-- and that is William Shakespeare.
Speaking of Shakespeare. Carlyle,
in his ``Heroes and Hero Worship ,'' rightly says,
``He is the grandest thing which we British people have yet done.''
If the great British Empire were destroyed tomorrow, a thousand years after this, when men read the works of Shakespeare,
they would say that the British nation was a nation with a very high civilization.

Indeed, as the one Latin word ``virtus'' -- not virtue in the English sense, but the virtue of the Japanese Samurai -- is a proof to those who understand Latin that the ancient Romans were a nation with a very noble civilization
-- so the English word ``gentleman'' alone, without any Shakespeare, is enough to show that the British nation is nation with even a finer civilization than the noble civilization of the ancient Romans, because it is a civilization which, tempered with the spirit and ideal of gentleness of Christianity,
has produced a type of humanity called a ``gentleman.''
For the chief and one aim of civilization is not to make and teach men to be strong,
but to make and teach men to be gentle;
in other words, to develop and produce not what Kipling calls coarse, vulgar, ``flannelled fools'' who can yell as the American Y. M. C. A. in China now trying to do
-- but to develop and produce gentlemen,
who, as we Chinese say, understand li-yo, courtesy, good manners or ``good form,'' as the Englishman calls it, and music.

Indeed, I may say here, it is because the ideal of the British or English civilization is to make a ``gentleman'' that the British people are the only modern people in the world today,
as I have said, who can govern an Empire. The great Soldier-Gentleman of Japan, Tokugawa lyeyasy,
after he had, with his sharp sword, cast the ``devil of cruelty'' out of old feudal Japan
-- just in the same way as the British ``Unknow Warrior.''
Whom they lately buried in Westminster Abbey in England,
has now cast the ``devil'' called Furor Teutonicus out of feudal Germany
-- was on his death-bed, he sent for his grandson lyemistsu and said to him,
``You are the man who one day will have to govern an empire.
Remember, the way to govern an empire is to have a gentle and tender heart
(the Latin alma as in alma mater, the extreme gentle tenderness of a mother).''

Now the reason, it seems to me, why the Japanese statesmen now find it so difficult to govern Korea,
is because the modern Japanese,
instead of reading and teaching their students the Guai Shi,
now read and teach them the pragmatic philosophy and political science of Professor Deway,
and have thus forgotten the essence of political science contained in those words of their great Shogun which I have just quoted.

In the same way, the reason why the British politicians now in England find it difficult to govern Ireland and India,
is because modern Englishmen today do not know that it was not British democracy,
the British Constitution or Parliamentarism,
but the British or English civilization with the ``gentleman'' and its ideal;
in short, that it was not the British mob, but the British or English gentleman who built up the great British Empire of today. But that is neither here nor there.

I have said that a nation is called a civilized nation only when it has a spiritual asset or ``realized ideals.''
Now let me ask, what ``realized ideals'' or spiritual asset have the Americans today to show in order to entitle them to be called a civilized nation?
In literature I know only one great name in America and that is Emerson.
But then even Emerson, as Matthew Arnold says, is not quite a great name in literature.
Without speaking of Homer, Virgil Dante and Shakespeare, Emerson is not a great name in literature even as Plato, Cicero Bacon and Voltaire are great names in literature.

Of poetry again, which, like music, is the highest expression of spiritual life in a nation,
I also know only one poem written by an American poet which can be truly called a real poem.
By a real poem I mean a poem which is all poetry and nothing but poetry;
a poem which becomes the spiritual asset of a nation and forms an important part of its civilization,
such as Gray's ``Elegy in a Country Churchyard'' and Robert Burns's ``Auld Lang Syne.''
Poems like the poems of the English Lord Macaulay are, although in meter and rhyme,
not poetry at all, but only rhetoric.
Now, the poems of even famous American poets like Longfellow and John Greenleaf Whittier are for the most part also rhetoric,
with some poetry in them: they are not all poetry,
not real poems, which like Robert Burns's ``Auld Lang Syne,'' can become the spiritual as set of a nation.
Indeed, as I have said, the only poem I know written by an American poet which can truly be called a real poem and can therefore become the spiritual asset of a nation,
is Edgar Allan Poe's ``\emph{Annabel Lee}.''

Now many people might think that I was only joking when in one of my articles lately I said
that reading the English nursery rhyme about Taffy the Welshman could help to educate the soul of a man.
But in all seriousness I meant what I said.
For poems like the English nursery rhymes are real poems,
but of course, real poems for children: and real poems have a magic in them which,
as Matthew Arnold says of Homer's poetry, can transmute and transform man.
If you don't believe this, you just ask a Japanese geisha to repeat the famous Chinese poem in Japanese,
``Tsuki ochi karasu naite shimo ten ni mitsu,'' and you will see that,
with her eyes suddenly becoming illumined and all her features suffused with ecstasy, she becomes,
for the moment, quite an other woman, more beautiful and charming than she really is. 

In other words, things like the English nursery rhymes are really the expression, in a small way, of a nation's spiritual life and form a part of its civilization.
Now, the fact that the Americans as a nation have no nursery rhymes is to me a proof positive
that the Americans as a nation have no spiritual life;
that they are still a nation, as I have said,
without any spiritual asset of civilization. 

Finally, then, if the United States were destroyed tomorrow,
I want to ask what great spiritual thing have the Americans as a nation done which they can leave behind them to show to men of after generations that they were once a nation with a civilization.
In my opinion, the only spiritual asset of the American Nation,
the only really spiritual things which the Americans as a nation have done that,
if they, as a nation were destroyed tomorrow,
will be remembered by men of after generations
-- are the work of Poe's ``Annabel Lee'' and the music of the plantation songs of the negroes in America.

Perhaps some people will say to me,
``What about the President Wilson's `Fourteen Points,'
which, like the Ten Commandments of Moses, will found a new religion to make the world safe for democracy,
and thus bring in the millennium?''
In reply to this I say that these Fourteen Commandments of President Wilson were made only two years ago,
and now even Mr. Lkoyd George has completely forgotten them! 

Last of all, speaking of President Wilson reminds me
that I have not asked what really great men have the Americans as a nation produced?
Everybody will, of course, answer, George Washington;
but even at the risk of mortally offending all my American friends,
I must say that to me George Washington,
although an admirable man in many ways, had yet, unfortunately,
like the American Pilgrim Fathers, a little too much of the ``moral prig'' in him to be really a great man
-- a really great character like the French Bayard or the English Sir Walter Raleigh and Philip Sydney.
Indeed, as Matthew Arnold, speaking of the American Pilgrim Fathers, says,
``Notwithstanding the mighty results of the Pilgrim Fathers' voyage,
they and their standard of perfection are rightly judged when we figure to ourselves Shakespeare and Virgil accompanying them on their voyage and think what intolerable company Shakespeare and Virgil would have found them''
-- so I , for my part, if I had to take a trip to Merry England in Shakespeare's time or in modern times to Japan, a man like George Washington would be the last man I would take with me as a companion,
for one could not think of taking such a man to the Windsor ``Garter Inn'' and introducing him to Mrs. Ford, Mrs. Anne Page, Bardolf, Pistol, Nym and others of that merry company, nor to a Geisha house in Japan! 

A Scotchman I met at the Pekin Pavilion the other night, who had lately returned from Scotland,
when I asked him whether he thought there was any likelihood of Scotland becoming dry,
like America, answered: ``No, certainly not.'' I asked him why.
``Because,'' he said proudly,
``Scotland is a country with a Robbie Burns. America can become dry because America is country which has never had a Robbie Burns.''
In the same way, to foreigners who, when I tell them that a big country like China cannot be a republic, say to me that America, also a big country, is a republic,
I answer, ``America can be a Republic because the Americans, unlike us Chinese, are a nation without any civilization, just as my Scotch friend says,
America can become dry because she is a country without a Robert Burns.''
In fact, China, I may say here, has become a republic now because the poor demented imbecile Republican Chinaman today has lost his civilization as he has lost his queue.
The reason again why the republic in China cannot work now,
is because not all Chinese have lost their civilization.

Now before I conclude, I want to say that my object in writing this article is not to abuse the American people.
The American people, I have tried to show, are still a nation without any civilization and that is because they are still a young nation.
To be young, as William Pitt in his famous speech in the British Parliament once said, is not an ``atrocious crime.'' Indeed because the Americans are a young nation living in a big country like America,
they have such great potentialities that I am inclined to think that,
if civilization can be saved after this great world upheaval,
the three great future empires of the world will be American, Russia and China. 

My object in writing this article, I say again, is not to abuse the American people.
My object is to tell people that the only way to save civilization
-- the first thing you must do if you want to save civilization
-- is to know what civilization is.

Indeed what made me write this article is because I read lately an essay written by the Prime Minister of Japan,
Mr. Hara, in which he said that he wanted to amalgamate the civilization of the East and West.
It seems to me, when he said that, the Prime Minister of Japan,
if I may be permitted to say so, does not know what is civilization.
For a civilization is either a true civilization or a false or,
as the Japanese say, a magai make-believe civilization:
there is no East or West. 

Confucius in his time was so sick of hearing people talk of civilization that he once said,
``Civilization, Civilization, is the cry now:
but are carrying fine jades and wearing silk dresses the whole of civilization?''
In the same way I take the liberty here of asking men like the Japanese Prime Minister who talk of amalgamating civilizations:
are wearing high collars, cutting off queues, building European houses,
riding in motor cars and erecting statues such as one sees in the streets of Tokio
-- the whole of civilization, or even civilization at all? Indeed, Matthew Arnold, speaking of Christianity
-- curiously using the very same words which the Chinese poet Su Tung-Po of the Sung dynasty used when speaking of Confucianism -- says,
``Christianity is, first and above all, a temper, a disposition
-- so I want to point out here that civilization also is first and above all, a state of the mind and heart:
a spiritual life. In the true sense of civilization, an ordinary Japanese Gelthar is more civilized than most American professors with all their pragmatic philosophy and political science.
In fact, civilization in its essence, is not dress, house, furniture, machine, ship or gun, but
-- gentleness of mind and heart or, in the words of the great Japanese Shogun which I have already quoted -- a gentle and tender heart.
Last of all then, I would like again the remind the Japanese people, who, in my opinion,
are now the real Se-i Shogun or Markgraf Nation, Military Guardian of Civilization in the Far East,
of the words of their great dead Shogun Tokugawa lyeyasu, who, when speaking to his grandson, was really speaking to the Japanese Nation today. 

\section{``Mad Monk of Russia''}
Recent news dispatches from Riga, Latvia, state that Iliodor,
the ``Mad Monk of Russia,'' Rasputin's former friend, is back in Tsaritzyn,
where the monastery built from the offerings of the people to him is located.
His presence in Russia was predicted by himself in a book published here by the Century Company in which
he revealed the story of his relations with Rasputin,
with the Czar and with the spies.
He stated his intention of going back,
believing his mission was to restore religion of the people under the revolution.

