
The object of this book is an attempt to interpret the spirit and show the value of the Chinese civilisation.
Now in order to estimate the value of a civilisation, it seems to me, the question we must finally ask is not what great cities, what magnificent houses, what fine roads it has built and is able to build;
what beautiful and comfortable furniture,
what clever and useful implements, tools and instruments it has made and is able to make;
no, not even what institutions, what arts and sciences it has invented:
the question we must ask, in order to estimate the value of a civilisation,
-- is, \emph{what type of humanity},
what kind of men and women it has been able to produce.
In fact, the man and woman,
-- the type of human beings
-- which a civilisation produces,
it is this which shows the essence, the personality,
so to speak, the soul of that civilisation.
Now if the men and women of a civilisation show the essence,
the personality and soul of that cifilisation, the language which a man and woman speak, shows the essence, the personality, the soul of the man and woman.
The French say of literary composition, ``\emph{Le style, c'est l'homme.}''
I have therefore taken these three things, the Real Chinaman, the Chinese woman and the Chinese language,
-- as the subjects of the first three essays in this volume to illustrate the spirit
and show the value of the Chinese civilisation.

I have added to these, two essays in which I have tried to show how and why men, foreigners who are looked upon as authorities on the subject, do not really understand the real Chinaman and the Chinese language. The Rev. Arthur Smith, who wrote the Chinese Characteristics, I have tried to show, does not understand the real Chinaman, because, being an American, --he is not deep enough to understand the real Chinaman. Dr. Giles again, who is considered a great sinologue,
I have tried to show, does not really understand the Chinese language, because, being an Englishman, he is not broad enough, -- he has not the philosophic insight and the broadness which that insight gives, I have wanted to include in this volume and essay I wrote on J. B. Bland and Backhouse's book on the famous late Empress Dowager, but unfortunately I have not been able to find a copy of that essay which was published in the ``National Review'' in Shanghai some four years ago.
In that essay, I have tried to show that, such men as J.B. Bland and Backhouse do not and cannot understand the real Chines woman, -- the highest type of woman produced by the Chinese civilisation viz the late Empress Dowager, because such men as J. B. Bland and Backhouse are not simple, -- have not the simplicity of mind, being too clever and having, like all modern men,
a distorted intellect. \footnote{Mencius says, ``What I hate in your clever men is that they always distort things. 所惡於智者為其鑿也'' Bk IV. Part II. 26.}
In fact, in order to understand the real Chinaman and the Chinese civilisation, a man must be deep, broad and simple, for the three characteristics of the Chinese character and the Chinese civilisation are: depth, broadness and simplicity.

The American people, I may be permitted to say here,
find it difficult to understand the real Chinaman and the Chinese civilisation,
because the American people, as a rule, are broad, simple, but not broad.
The Germans again cannot understand the real Chinaman and the Chinese civilisation because the Germans, especially the educated Germans, as a rule, are deep, broad, but not simple.
The French, -- well the French are the people, it seems to me, who can understand 
and has understood the real Chinaman and the Chinese civilisation best.
\footnote{The best book written in any European Language on the spirit of the Chinese civilisation is a book
called ``La Cit\'e Chinoise'' by G. -- Eug. Simon who was once French Consul in China.
It was from this book that Prof. Lowes Dickinson of Cambridge, as he himself told me,
drew his inspiration in writing his famous ``Letters from John Chinaman.''}
The French, it is true, have not the depth of nature of the Germans nor the broadness of mind of the Americans nor the simplicity of mind of the English,
-- but the French, the French people have to a preeminent degree a quality of mind
such as all the people I have mentioned above as a rule, have not,
-- a quality of mind which, above all things, is necessary in order to understand the real Chinaman and the Chinese civilisation;
a quality of mind viz: \emph{delicacy}.
For, in addition to the three characteristics of the real Chinaman and Chinese civilisation
which I have already mentioned,
I must here add one more, and that the chief characteristic, namely delicacy;
delicacy to a preeminent degree such as you will find nowhere else except perhaps among the ancient Greeks and their civilisation.

It will be seen from what I have said above that the American people if they will study the Chinese civilisation, will get depth;
the English, broadness; and Germans, simplicity;
and all of them, Americans, English and Germans by the study of the Chinese civilisation, of Chinese books and literature, will get a quality of mind which,
I take the liberty of saying here that it seems to me, they all of them, as a rule,
have not to a preeminent degree, namely, \emph{delicacy}.
The French people finally, by the study of the Chinese civilisation,
will get all, -- depth, broadness, simplicity and a still finer delicacy than the delicacy which they now have.
Thus the study of the Chiness civilisation, of Chinese books and literature will,
I believe, be of benefit to all the people of Europe and America.
I have therefore added to this volumen an essay on Chinese scholarship, -- the sketch of a programme how to study Chinese, which I made for myself when I made up my mind and began,
after my return from Europe, to study the civilisation of my own country,
exactly now thirty years ago;
this sketch of a programme how to study Chinese and the Chinese civilisation.

Last of all, I have included as an appendex an essay on pratical politics,
-- an essay on ``The War and the Way out.''
Knowing full well the danger of entering into the arena of pratical politics,
    I nevertheless do it, because in order to prove the value of the Chinese civilisation, I want to show how the study of the Chinese civilisation can help to solve the problem facing the world to-day, -- the problem of saving the civilisation of Europe from bankruptcy.
In fact I want to show that the study of Chinese, of Chinese books and Chinese literature is not only a hobby for sinologues.

In this essay, I have tried to show the moral causes which have brought on this war;
for until the ture moral causes of this war are understood and remedied,
there can be no hope of finding a way out of it.
The moral causes of this war, I have tried in my essay to show, are the \emph{worship of the mob} in Great Britain and the \emph{worship of might} in Germany.
I have, in my essay, laid emphasis more upon the worship of the mob in Great Britain, than the worship of might in Germany,
because looking impartially upon the question, it seems to me that it is the worship of the mob in Great Britain, which is responsible for the worship of might in Germany;
in fact, the worship of the mob in all European countries and especially in Great Britain,
it was this which has created the enormous German Millitarism which everybody now hates and denounces.

Now let me first of all say here that it is the \emph{moral fibre} in the German nation, their intense love of righteousness and, as a consequence, their equally intense hatred of unrighteousness,
hatred of all untidiness and disorder (Unzucht und Unordnung),
which makes the German people believe in and worship might.
All men who intensely love righteousness,
who intensely hate unrighteousness are inclined to believe in and worship might.
Why? Because Carlyle with the German moral fibre in him intensely hated unrighteousness.
Now the reason why I say that it is the worship of th emob in Great Britain
which is responsible for the worship of might in Germany,
is because, the \emph{moral fibre} -- the intense hatred of unrighteousness,
of untidiness and disorder in the German nation makes them hate the mob,
the worship of the mob and the mob worshippers in Great Britain.
After the German nation saw how the mnob and the mob-worshipping politicians of Great Britain made the Boer War in Africa,
their \emph{instinctive} intense hatred \footnote{The famous telegram of the German Emperor to President Kruger was an \emph{instinctive} outsburst of indignation of the true Gernamic soul with its moral fibre against Joseph Chamberlain and his Cockney class in England, who manipulated the Boer War.}
for the mob, the mob-worship and the mob-wroshippers in Great Britain made the German nation willing to make heavy sacrifices, make the \emph{whole German nation ready to starve themselves to create a Navy} with the hope to put downn the mob,
the mob-worship and mob-worshippers in Great Britain.
In fact, the German nation, I may say, found themselves surrounded on all sides by the mob, mob-worship and mob-worshippers encouraged by Great Britain in all Europe and this made the German nation believe more and more in might,
made the German nation worship might as the only salvation for mankind.
This worship of might in Germany created by the hatred for the Religiion of mob worship in Great Britain, thus created the enormous monstrous German Militarism which everybody now hates and denounces.

Thus, I say again, it is the worship of the mob, the Religion of the worship of the mob in all European countries, especially in Great Britain, which is responsible for the worship of might in Germany;
which has created the abnormous enormity and monstrosity of German Militarism in Europe to-day.
If therefore the people in Greate Britain and the people in all European countries and America want to put down German Militarism, -- they must try first to put down the mob, the mob-worshippers and the Religion of mob-worship in their own countries.
\footnote{Confucius said to a disciple ``when outside nations are dissatisfied with you, you should cultivate \emph{civil or Civic} virtues (遠人不服則修文德).''
The Brithish aristocracy, however, like the Manchu aristocracy in China, are now helpless against the mob and mob worshippers in England.
But it is, I must say, a great credit to the British aristocracy that not one of them as far as I know, has joined the mob in England in their shout, howl and yell in this war.}
To the people of Europe and America, and in Japan and China too, to-day who speak of and want liberty, I will venture here to say that the only way, it seems to me, to get liberty, true liberty is to behave themselves;
to learn to behave themselves properly.
Look at China before this Revolution.
There was more liberty among the Chinese people,
-- no priest, no policeman, no Municipal tax,
no income tax to bother them -- more liberty among the Chinese than among any other people in the world;
and why? Because the Chinese people before this Revolution behaved themselves;
knew how to behave themselves;
knew how to behave themselves as \emph{good citizens}.
But now after this Revolution -- there is less liberty in China, and why?
Because the modern queueless, up-to-date Chinamen,
the returned students have learnt from the people of Europe and America,
-- learnt from the European mob in Shanghai how to \emph{misbehave themselves};
to behave themselves not as good citizens,
but as a \emph{mob} -- a mob encouraged, coddled and worshipped by the British diplomats and the British Inspector General of Customs in Peking.
\footnote{To show what a mob the Chinese returned students have became, i may mention here that some of these students in Peking last year actually wrote letters to the ``Peking Gazette,'' a newspaper conducted by a clever Chinese ``Babu'' by the name of Eugene Chen, openly threatening to organise and carry out a public assault upon me for criticising the new Chinese woman in my essay on ``the Chinese worman.'' This clever Chinese ``Babu'' Eugene Chen the instigator of the contemplated piece of rowdyism now is a respected member of the Committee of the Anglo-Chinese Friendship Bureau under the patronage of the British Minister and the I. G. of the Chinse Customs!}
In fact, what I want to say here is, that if the people in Europe, the people in Great Britain want to put down German Militarism, Prussian Militarism,
they must keep the mob in their own countries in order;
they must make the mob in their own countries behave themselves properly;
in fact they must put down the Religion of mob-worship,
and the mob-worshippers in their own countries.

But now while I say that the British people with their mob worship and encouragement of mob-worship are responsible for the worship of might in Germany,
for German Militarism, I must at the same time say here that,
looking again impartially upon the question, it seems to me that the \emph{direct}
responsibility for this war nests more heavily upon the German people,
upon the German nation, than upon anybody else.

In order to understand this, let the first of all here give the history of German Militarism in Europe.
After the Reformation and the Thirty Years War,
the Germanic nations, the people of the Germanic race with their \emph{moral fibre},
with their intense love of righteousness and their intense hatred of unrighteousness,
hatred of all untidiness and disorder, the German people, with Militarism as a sword in their hand,
became the rightful guardian of civilisation in Europe.
In other words, the responsibility for putting order and tidiness (Zucht und Ordnung) in Europe;
in fact, the \emph{moral hegemony} so to speak of Europe came into the hands of the German people.
After the Reformation, Frederick the Great, like Cromwell in England, had to take up and use the sword of German Militarism to put order and tidiness in Europe and he succeeded in putting order and tidiness at any rate in the Northern part of Europe.
Now see what happened after Frederick the Great's death.
His successor did not know how to use the sword of German militarism in order to guard and protect the civilisation of Europe;
in fact, he was unfit to hold the moral hegemony of Europe.
The result was, the whole of Europe, even the courts in Germany became a bottomless pit of abominations covered up only with the veneer of civilisation;
so much so that at last the suffering population, the plain men and women in France rose up with pikes to protest against the abominations.
The plain men and women in France who rose up to protest against the abominations very soon became a \emph{mob}, and this mob finally found a great and able leader,
Napoleon Bonaparte, \footnote{Emerson with great insight, says, ``What sent Napoleon to St. Helena, was not loss of battles, but the \emph{parvenu}, the vulgar ambition in him -- the vulgar ambition to marry a real Princess, to found a dynasty.''}
who led them to rob, murder, kill and ravage all Europe until the nations in Europe rallying round the small nucleus of \emph{sound} German Militarism left in Europe,
put an end to the career of the great leader of the mob at Waterloo.
After this the mnoral hegemony of Europe should have returned to the people of the Germanic race, to the Prussians, the back bone of the German nations.
But the jealousy of the other races which formed the Austrain Empire prevented this.
The result was that without the German nation with its moral fibre and the sword of German Militarism to keep down the mob, the mob in 1848 again rose up furiously to break the civilisation, of Europe.
Then again the German nation -- the backbone of the Germanic nations,
the Prussians with their moral fibre and the sword of German Militarism, saved Europe, -- saved Kingship, (Bismarck called it the dynasty), saved civilisation in Europe from the mob.

But now the Austrians, -- the other races forming the Austrian Empire again became jealous and would not allow the German nation, -- the backbone of the Germanic nation, Prussia to take ove the moral hegemony of Europe until 1866 when the Prussian King Wilhelm with Bismarck and Moltke had to put down the Austrian jealousy by force and took over the hegemony into their hands.
After this, Louis Napolean, not like his great uncle a leader, but a swindler of the mob or, as Emerson calls him, a successful thief, tried with the mob of Paris behind him, to dispute and wrest the moral hegemony of Europe from the German nation.
The result was that the Emperor Wilhelm with the sharp sword of German militarism in his hand had to march to Sedan and put down the poor successful thief and swindler of the mob.
The plain men and women of Paris who put their trust in the mob and the swindler of the mob had their houses sacked and burnt \emph{not by the German Militarism}, not by the Germans and Prussians, but by the very mob in whom they put their trust.
After 1872, -- not only the moral, but the actual political hegemony of Europe passed finally into the hands of the German nation with the moral fibre of the Germanic race in their soul and the sword of German Militarism in their hand,
to hold down the mob and keep the peace in Europe and thanks to the moral fibre in the German nation and the sword of German Militarism, Europe since 1872 has now enjoyed peace for 43 years.
Thus people who abuse and denounce German Militarism and Prussian Militarism should remember how much Europe owes to this very German, this Prussian Militarism which they now abuse and denounce.

I have in the above taken the trouble to give this rough short sketch of the German Militarism in Europe in order to make the German people see that I am not prejudiced against them in saying what I am going to say to show that the actual \emph{direct} responsibility for this war rests more heavily upon them,
upon the German people and German nation than upon anybody else.
I say that the actual \emph{direct} responsibility for this war rests more heavily upon the German people and German nation than upon anybody else;
and why? -- Because \emph{power means responsibility}.\
\footnote{Confucius says, ``Possession of power without leniency and generosity is a thing which I never can bear to see. (居上不寬吾何以觀之) Shakespeare says: ``Oh, it is glorios to have a giant's strength: but it is tyrannous to use it like a giant.''}

I say that it is the intense love of righteousness, the intense hatred of unrighteousness, intense hatred of all untidiness and disorder (Unzucht und Unordnung) in the German people which makes them believe in and worship might.
Now I want to say here that this hatred of unrighteousness, hatred of untidiness and disorder, when it becomes over-intense, when it is carried to excess becomes also an \emph{unrighteousness}, becomes a frightful and terrible unrighteousness, something more sinful and wrong even than untidiness and disorder.
It was this over intense hatred of unrighteousness which came from their intense love of righteousness, the intese, narrow, hard, rigid hatred of unrighteousness carried to excess in the old Hebrew people -- the Hebrew people to whom the people of Europe owe their knowledge and love of righteousness, it was this which destroyed the Jewish nation.
It was from this over-intense narrow, hard, rigid hatred of unrighteousness that Jesus Christ came to save Hist people.
Christ, with what Matthew Arnold calls his unspeakable sweet reasonableness said to his own people: ``Learn of me, that I am \emph{mild} and lowly and yet shall have peace in your souls.'' But the Jews -- his own people would not listen to him;
they, instead of listening to him, crucified him and the consequece was --
the Jewish nation perished.
To the Romans who were then the guardians of civilisation in Europe, Christ said, ``All they that take the sword shall perish with the sword!''
\footnote{That is to say, all who depend and put their faith solely upon material brute force or as Emerson says, who believe in the vulgar musket worship.}
But the Romans would not listen, but instead, all owed the Jews to crucify him.
The consquence was -- the Roman Empire and the old civilisation of Europe perished and passed away.
Goethe says: ``What a long way mankind must have travelled before they came to know how to deal gently even with sinners, to be merciful to law-breakers,
\emph{and to be human even to the inhuman}.
Truly they were men of Divine nature who first taught this and who gave their lives for it in order to make the realisation of this possible and to hasten the practice of it.
``(Welchen Weg musste nicht die Menschheit machen, bis sie dahin gelangte, auch gegen Seluldige gelind, gegen Verbrecher schonend, gegen auch Unmenschliche menschlich zu sein. Gewiss waren as Manner g\"ottlicher Natur, die dies zuerst lehrten, die ihr Leben damit zubrachten, die Aus\"ubung m\"oglich zu machen und zu beschleunigen.)''

With those words of their great Goethe I will endure here to appeal to the German people, to the Germann nation and say to them that,
unless they find a way to put down their narrow, hard, rigid, excessive hatred of unrighteousness which makes them believe so absolutely in and worship might,
unless they put away their absolute belief in and worship of might -- they, the German nation, like the Jewish nation, will perish and what is more,
the modern civilisation of Europe for want of a strong guardian, will collapse and pass away just as the ancient civilisation of Europe passed away.
For it is this overintense, narrow hard, rigid hatred of unrighteousness which makes the German people, the German nation believe in and worship might;
and it is this absolute belief in and worship of might which makes the German nation, the German diplomats German officials and the German people so inconsiderate and tactless in their behaviour towards other people.
When my German friends have asked me to show them a proof of the German worship of might, of German tactlessness, I have simply pointed the Kettler memorial in Peking to them.
The Kettler memorial in Peking is a standing monument of the German worship of might, of the tactlessness of the German diplomacy,
the tactlessness of the German nation in their international dealings with other nations.
\footnote{The German Minister Baron Kettler during the fanatic Boxer outbreak in China was accidentally killed by a madman from the fanatic soldiery.
As a punishment for this act of a mad man, the German diplomats insisted upon brandding the whole Chinese nation on the forehead with an indelible mark of humiliation, by having this kettler memorial erected in the principal street of the Chinese Capital.
See note on Page 12. The later Count Cassini, Russian Minister in Peking just before the Boxer outbreak, said in an interview with an American journalist,
``The Chinese are a \emph{polite people}, but the impoliteness of the British and German Ministers, -- especially of the German Minister in Peking is something outrageous.''
}
It was this worship of might of the German nation, this tactlessness of the German diplomacy of which the Kettler memorial is a standing monument, which made the Emperor of Russia say: ``We have stood this for seven years; now it must finish;''
this tactlessness of the German diplomacy which made the really peaceloving Emperor of Russia and the best people in Europe,
the soundest, most loveable, kindest and most generous-hearted people in Europe the Russians take the side of the mob and mob-worshippers in Great Britain and in France, which created the Triple-Entente;
which made the Russians finally take the side even of the anarchic mob in Servia and thus brought on this war.
In one word it is this tactlessness of the German diplomacy, of the German people, of the German nation which is \emph{directly} reponsible for this war.

I say therefore, if the German nation at this moment the true,
rightful and legitimate grardian of the modern civilisation of Europe to-day,
is not to perish and the mnodern European civilisation is to be saved,
-- the German nation, the German people must find a way to put down their over-intense, narrow, hard, rigid hatred of unrighteousness which makes them believe so absolutely in and worship might;
in fact they must find a way to put down their absolute belief in and worship of might which makes them so inconsiderate and tactless.
But then, where are the German nation, the German people to find a way to put down their absolute belief in and worship of might?
The German nation, the German people, I say, will find this in these words of their great Goethe.
Goethe says: ``\emph{There are two peaceful powers in this world: Right and Tact.}'' (Es gibt zwei friedliche Gewalten auf der Welt: Das Recht und die Schicklichkeit.)

Now this Right and Tact, \emph{das Recht und die Schicklichkeit},
is the essence of the Religion of good citizenship which Confucius gave to us Chinese here in China;
this Tact, this \emph{Schicklichkeit}, especially, is the essence of the Chinese civilisation.
The Religion in the civilisation of Right, but it did not teach Tact.
The civilisation of Greece taught the people of Europe the knowledge of Tact but it did not teach Right.
But the Religion in the civilisation of China teaches us Chinese both Right and Tact, -- das recht und die Schicklichkeit.
The Hebrew Bible, the plan of civilisation according to which the people of Europe to love righteousness, to be righteous men, to do right.
But the Chinese Bible -- the Five Canons and Four Books in China,
the plan of civilisation which Confucius saved for us the Chinese nation, teaches us Chinese also to love righteousness;
to be righteous men; to do right, but it adds: ``Love righteousness, be righteous men, do right -- but \emph{with good taste}.''
In short, Religion in Europe says: ``Be a good man.''
But the Religion in China says: ``Be a good man \emph{with good taste}.''
Christianity says: ``Love Mankind.''
But Confucius says: ``Love Mankind \emph{with good taste}.''
This Religion of righteousness with good taste, which I have called the Religion of good citizenship, is the new religion I belive,
which the people of Europe, especially the people of the countries now at war,
want at this moment not only to put an end to this war,
but to save the civilisation of Europe,
to save the civilisation of the world.
This new Religion, the people of Europe will find here in China,
-- in the Chinese civilisation.
I have therefore in this little book made the attempt to interpret and show the value of this,
-- the Chinese civilisation.
I do this with the hope that all educated serious thinking people,
who read this book of mine will, by reading this book, better understand the moral causes of this war and understanding the moral causes of this war,
will all help to put an end to this cruel, inhuman, useless and most monstrous war which the world has ever seen.

Now if we want to help to put an end to this war,
we must, all of us, try to put down first the 
worship of the mob and then the worship of might 
in the world to-day, which, as I have said, are the 
cause of this war. We can put down the worship of 
the mob, only when in our daily life, in everything 
we say and do, every one of us will think, not of 
interests, of expediency -- \emph{of what will pay}, but think 
of that word in Goethe's saying -- \emph{Right}. Confucius 
says: ``The gentleman understands \emph{right}; the \emph{cad}
understands \emph{interests}, -- \emph{what will pay}.''
Further we can only put down the worship of the mob in the world 
when we have the courage, even if it does not pay to 
do so, to refuse to join and go in with the crowd -- with 
the \emph{mob}. Voltaire says: ``C'est le malheur des gens 
honn\^etes qu'ils sont des laches.
It is the mirfortune of so-called good people that they are cowards.''
For it is the selfishness and cowardice in all of us,
I want to say here, selfishness which makes us think of 
interests, of expediency, of what will pay, instead of 
right, and cowardice which makes us afraid to stand 
up alone against the crowd, against the mob,
-- it is this selfishness and cowardice in all of us which has given 
rise and created the mob and the worship of the mob 
in the world to-day. People say German Militarism 
is the enemy and danger of the world to-day.
But I say it is the selfishness and cowardice in all of us 
which is the real enemy of the world to-day : selfishness 
and cowardice in all of us, which, when combined, 
becomes Commercialism.
It is this spirit of Commercialism, in all countries of the world,
especially in Great Britain and America,
which is 
the real enemy of the world to-day.
It is, I say, this spirit of Commercialism in all of us and not 
Prussian Militarism which is the real, the greatest 
enemy of the world to-day. For it is this Commercialism, 
a combination of selfishness and cowardice which has 
created the Religion of the worship of the mob 
and it is this Regigion of the worship of the mob 
in Great Britain which has created the Religion 
of the worship of might in Germany, created the 
German Militarism which, as I said, firrally brought 
on this war. \emph{The fons et oriyo} of this war, I say, 
therefore is not militarism, but \emph{Commercialism}, which, 
as I said, is a combination of selfishness and 
cowardice in all of us.
Thus, if we want to help to put an end to this war,
we must, all of us, first put down the spirit of Commercialism,
the combination of selfishness and cowardice in us;
in short, we must first of all, think of \emph{right} and not of interests and 
then have the courage to stand up against the crowd, 
against the mob.
In this way, I say, and \emph{only in this way} we can help to put down the worship of 
the mob, the Religion of the worship of the mob and 
in putting down this worship of the mob, this 
Religion of the worship of the mob, we can help to 
put an end to this war. 

Now as soon as we have put down the worship of 
the mob, it will then be very easy to put down the 
worship of might, easy to put down German Militarism, 
put down Prussian Militarism.
The only thing we will have to do, in order to put down the worship 
of might, to put down German, Prussian or any 
Militarism in the world, is to think of the other 
word in that saying of Goethe -- \emph{Schicklichkeit, Tact, 
Good Taste} and, in thinking of that, to behave 
with tact and good taste, in short to behave 
properly;
for might, Militarism, even Prussian 
Militarism can do nothing and will soon find itself 
useless and unnescessary against people who know 
how to behave themselves properly.
This then is the 
essence of the Religion of good citizenship; this is the 
secret of the Chinese civilisation. This is also the 
secret of the new civilisation of Europe which the 
German Goethe gave to the people of Europe and the 
secret of this civilisation is: to put down force, \emph{not} by 
force, but by \emph{right and tact};
in fact to put down force 
and everything that is evil in this world, not by force, 
but by ordering our conversation aright and behaving
ourselves properly;
and ordering our conversation
aright and behaving properly means \emph{to do right and to
behave with tact and good taste}. 
\footnote{Confucius says, ``The moral man, the gentleman by living a life 
of simple truth and earnestness can bring peace to the world (君子篤恭而天下平).}
This is the secret, the 
soul of the Chinese civilisation, the essence of the 
spirit of the Chinese people, which I have tried in this 
book to interpret and explain. 

Finally I will here conclude with the words with 
which I concluded the book ``Papers from a Viceroy's 
Yamen'' which I wrote after the Boxer trouble in China.
They are the words of the French poet 
B\'eranger and I think they are very appropriate at 
the present moment.

\begin{quote}
J'ai vu la Paix descendre sur la terre,

Semant de l'or des fleurs et des \'epis;

L' air \'etait calme et du Dieu de la guerre

Elle \'etouffait les foudres assoupis.

Ah! disait-elle, egaux par la vaillance.

Anglais, Francais, Belge, Russe ou Germain,

Peuples, formez une sainte alliance

Et donnez vous la main!
\footnote{我目睹和平徐徐降臨，

她把金色的花朵麥穗灑遍大地：

戰爭的硝煙已經散盡，

她抑制了使人昏厥的戰爭霹靂。

啊！她說，同樣都是好漢，

英法比俄德人

去結成一個神聖同盟

拉起你的手吧！

-- 據黃興濤譯文，下同。編者注。
}
\end{quote}

\myprefaceauthor{Ku Hung-Ming}{Peking}{20th April, 1915}
