
\begin{thebibliography}{}

\bibitem[A.~L. Avakyan et.~al. (1982)]{Ava1}
Avakyan, A. L., Zhevago, N. K. and Yan, Shi, (1982)
``Radiation from electrons and positrons at axial quasi
channeling'', {\it Zh. Eksp. Teor. Fiz.} {\bf 82}, 573; also in
{\it Soviet Physics JETP} {\bf 55}, 341.

\bibitem[R.~O. Avakyan et.~al. (1982)]{Ava2}
Avakyan, R.~O., Miroshnichenko, I. I., Murrey, D.
and Figut, T. (1982) ``Radiation from ultra-relativistic
positrons moving in a single crystal near axes and planes'',
{\it Zh. Eksp.Teor. Fiz.} {\bf 82}, 1825.  

\bibitem[A.~E. Avetisyan  et.~al. (1983)]{Ava3}
Avakyan, R. O., Avakyan, E. O., Avetisyan A. E. et
al. (1983) ``Radiation from high-energy electrons moving near
crystalographic axes and planes in diamond crystal'', {\it
Second All-Union Conference on Radiation of Relativistic
Particles} in {\it Crystals. Cheget.}  

\bibitem{Aga1} 
Aganyanz, A. O., Vartanov, Yu. A., Vartapetyan, G.
A. {\it et~al.}  (1983) ``Spectral-angular distribution of radiation
from electrons with energy 4.3~GeV for small angles of incidence
in diamond crystals'', Erevan, 1983, preprint Erevan Physics 
Institute No. 666(56).    

\bibitem{Ade1}
Adeishwilli, D. I., Bochek, G. L., Vitjko, V. I. et
al. (1984) ``Ionization and radiation energy losses of
relativistic electrons in silicon single crystals'', {\it Yad.
Fiz.} {\bf 40}, 318.

\bibitem{Adl1}
Adler, S. L., Bahcall, J. N., Callan, C. G. and
Rosenbluth, M. N. (1970) ``Photon splitting in a strong magnetic
field'', {\it Phys. Rev. Lett.} {\bf 25}, 1061.

\bibitem{Adl2}
Adler, S. L. (1971) ``Photon splitting and photon
dispersion in a strong magnetic field'', {\it Ann. Phys.} {\bf
67}, 599. 

\bibitem{Alg1}
Alguard, M. J., Swent, R. L., Pantell, R. H. {\it et~al.} 
(1980) ``Radiation from channeled leptons'', {\it Nucl. Instr.
Meth.} {\bf 170}, 7.

\bibitem{Alf1}
Alferov, D. F., Bashmakov, Yu. A. and Bessonov, E.
G. (1972) ``On a radiation of relativistic particles in
undulators'', {\it Zh. Tech. Fiz.} {\bf 42}, 1921.

\bibitem{Alf2}
Alferov, D. F., Bashmakov, Yu. A. and Bessonov, E.
G., (1975) ``Undulator radiation'', {\it Proc. (Tr.)} Lebedev
Phys. Inst. {\bf 80}, 100. 

\bibitem{And1}
Andersen J. U., Andersen S. K. and Augustyniak W.
(1977) ``Channeling of electrons and positrons'', {\it Mat. Fys.
Medd. Dan. Seals}. {\bf 39}, (10), 3.

\bibitem{And2}
Andersen, J. U., Bonderup, E., Laegsgaard, E. et
al. (1982) ``Axial channeling radiation from MeV electrons'',
{\it Nucl. Instr. Meth}. {\bf 194}, 209.           

\bibitem{Ani1}
Animalu A. (1977) {\it Quantum Theory of
Crystalline Solids}, Prentice-Hall, New Jersey.

\bibitem{Alf3}
Alferov, D. F., Bashmakov, Yu. A. and Bessonov, E.
G., (1975) ``Undulator radiation'', {\it Proc. (Tr.)} Lebedev
Phys. Inst. {\bf 80}, 100. 

\bibitem{And3}
Andersen J. U., Andersen S. K. and Augustyniak W.
(1977) ``Channeling of electrons and positrons'', {\it Mat. Fys.
Medd. Dan. Seals}. {\bf 39}, (10), 3.

\bibitem{And4}
Andersen, J. U., Bonderup, E., Laegsgaard, E. et
al. (1982) ``Axial channeling radiation from MeV electrons'',
{\it Nucl. Instr. Meth}. {\bf 194}, 209. 

\end{thebibliography}

